\ppse{} - A Peer-to-Peer Support for Multiplayer Games

### 2008-10-03 trunk/textos/p2pse-sbgames2008/ppsg.tex
corrections

\newcommand{\ppse}{Proj48534}
\newcommand{\hoverkill}{HK48534}

@@

\author{JEMS Manuscript Number 48534}
\contactinfo{48534@JEMS}
% %% Author and Affiliation (multiple authors). Use: and between authors
% \author{Felipe J. Vilanova, Carlos Eduardo B. Bezerra , Marcos R. Crippa, Fábio R. Cecin, Cláudio F. R. Geyer\\
%           Universidade Federal do Rio Grande do Sul\\
%           Bento Gonçalves, 9500\\
%           Porto Alegre, RS, Brazil\\
%           +55 (51) 3316 0000
% }
% \contactinfo{\{fjvilanova, carlos.bezerra, mrcrippa, fcecin, geyer\}inf.ufrgs.br}

@@

Multiplayer games are a very popular game genre, due to their highly interactive nature. Among those games, a class that is growing in popularity is MMOGs (Massively Multiplayer Online Games). MMOGs are real-time multiplayer games played through the Internet, where a great number of players (usually thousands) play within a persistent-state virtual world. Successful examples include EverQuest \cite{everquest} and World of Warcraft \cite{worldofwarcraft}.

@@

The main disadvantage of the client-server model is the lack of scalability. The cost of maintaining the server-side becomes excessive with the increase in the number of clients. When talking about commercial games, the usual approach is to continuously expand the number of machines on the server-side. That is a reasonable solution, however it is not suitable for projects on a budget such as those from small companies or research groups.

@@

In this paper a hybrid model is proposed, combining the security and consistency of the client-server model with the scalability and flexibility of the distributed model. In sections \ref{sec:c-smodel} and \ref{sec:p2pmodel} we discuss the client-server and peer-to-peer models. The \ppse{} %(acronym in portuguese for ``P2P for Entertainment Software'') 
architecture is explained in section \ref{sec:p2pse}. Section \ref{sec:simulations} presents the simulations we made to compare client-server and peer-to-peer models. Section \ref{sec:conclusion} presents conclusions on the topic.

@@

There is a growing interest in research and development of peer-to-peer architectures for MMOGs. The models proposed seek decentralization as a way of increasing scalability and reducing dependency on nodes in trusted areas. Other benefits include the elimination of central points of failure, as well as the increase of responsiveness.

@@

Guild Wars, as far as we can tell, follows the client-server model. Our proposal, which is illustrated in Figure \ref{fig:instanced}, is to use the instanced game model with a hybrid network architecture model. Since the interactions on the social space (chatting, trading) don't require high consistency, and there is a necessity for validation of who can play (game accounts, passwords), the server-side will be responsible for coordinating this part of the game. So even a server-side with modest processing capacity and network bandwidth could manage the social space if game quality is scaled down accordingly, for instance by sending less frequent updates to clients. The game sessions would be processed only on the client-side machines, avoiding unnecessary processing and communication cost on the server-side. The clients would form groups, wich would operate within a peer-to-peer dynamics.

@@

\begin{figure} 
  \centering 
  \includegraphics[width=1.0\linewidth]{images/p2pse.pdf}
 \caption{\ppse{} Architecture} 
 \label{fig:p2pse} 
\end{figure}

@@

The first layer in the \ppse{} architecture is responsible for forming the mesh of point-to-point connections. The client's connections with the servers and with other clients are established and managed in this layer. The basic network functions for connection establishment, such as socket creation, connection and packet sending and receiving, are given by a low-level API provided by the ZIG library \cite{zige} which basically implements a protocol that resembles SCTP \cite{stewart2000sct} over UDP.

The Layer 0 server is responsible for managing connections with all clients. Naturally, it maintains a list of all clients that are connected to it along with a logical communication endpoint object for each client. When started, the server spawns a socialization space called the social space object. All clients that are not in an action space are bound to the social space. All communication between clients that are in the social space is intermediated by the server.

The server can create new groups called action spaces, and it can destroy such existing groups. In the action spaces, clients communicate directly, and this requires all clients to already have the ability to send UDP packets to each other. The group object also allows clients of that group to broadcast messages to the whole group. Connection between group members is carried out through Peer objects. The clients, when in groups, maintain a list of Peer objects which is pretty much the same as the list of Client objects in the server, allowing peers to manage their connection with each other group member.

Layer 0 is also responsible for detecting connection timeouts. If a communication channel (client-server or peer-to-peer) has been without traffic for a specific amount of time, it is assumed to be dead and is terminated, generating a callback for the upper layer. To prevent alive links from dying, Layer 0 employs keep-alive messages.

@@

We see two main problems that can cause a connection failure between two peers: NAT/Firewall block and bandwidth insufficiency. When the Layer 0 indicates that a message must be send from one peer to another, Layer 1 must verify if there is a direct connection between the peers. If this connection doesn't exist, an alternative path must be discovered, using intermediate peers. After the path is discovered, the proper routing of the message can take place.

@@

Depending on the game, the resulting conflicts from a lack of centralized timestamping of movement and similar events, whenever they ensue, can be either handled by each peer individually or left for the super-peer to detect it and issue a special correction message later, as the BZFlag protocol does \cite{pellegrino2003bra}. Local corrections are an option if each peer is authoritative over its own avatar's position and if it broadcasts position updates for its own avatar. For instance, if a peer's local avatar overlaps with a remote peer's, the local avatar can push its own avatar out of that position. The remote avatar will do the same. The only issue is ensuring that the correction step won't make both peers try to resolve the situation by unstucking their avatars to the same spot again. This local conflict resolution is what we are currently employing in our capture-the-flag action prototype, \hoverkill\ (reference blinded).%Hoverkill \cite{hoverkill}.

@@

In this project we tried a somewhat unique approach. Since most events would be still centralized at the super-peer and most action games have one-per-client avatar position updates as their consistency, bandwidth and latency bottlenecks, we just left peers with total control over their positions and with the responsibility for sending them directly to other peers in a broadcast fashion. This optimizes for consistency and latency, and doesn't create a bandwidth bottleneck at the super-peer. On top of that, we tried AI-based detection of unusual patterns over streams of position updates coming from each peer. The main motivation was to detect blatant speed-cheating being performed by players while other players (without admin powers, nevertheless) quit the game in frustration. It was not our goal to prevent subtle position manipulation, since we wanted to avoid false positives more than we wanted to prevent any form of position cheating.

We have trained, using back-propagation, an Artificial Neural Network (ANN) over traces of gameplay generated from \hoverkill\ play sessions, which is our actual game prototype. We obtained some positive initial results [reference blinded]%\cite{gaspareto2008nna}
,  but we also found that a successful ANN detection engine is tied to many dynamic parameters, including specific game rules and maps, general behavior of game players (if it changes over time, the network must be re-trained), quality of the traces (they must cover all the detectable patterns and with enough variation), and others. The results put some merit on the general idea that using an automatic detection engine, instead of human attention, to discourage illegal position manipulation during gameplay could enable more simple and efficient but vulnerable protocols such as ours to still succeed in a real MMOG deployment scenario.

@@

The main purpose of the security module is to provide secure communications between server and clients, and between peer clients. Our security module is almost completely transparent to the application, both in terms of API and in network and CPU overhead. The module does many tasks behind the scenes, such as crypto key distribution and secure channel handshakes, tending to each application's individual needs for message confidentiality, integrity and authenticity.

The implementation works mainly by intercepting any engine UDP packets before they are written to the UDP socket for sending. In each packet, a small header is inserted with control information and, upon first contact between two parties (being them clients, servers or both), that message is delayed while another quick message exchange is performed for setting up the secure channel on-the-fly. The root Certificate Authority (CA) of the crypto system is the operator of the master server.

@@

\begin{figure} 
  \centering 
  \includegraphics[width=1.0\linewidth]{images/upload.pdf}
 \caption{Upload bandwidth utilization by the server} 
 \label{fig:upload} 
\end{figure}

\begin{figure} 
  \centering 
  \includegraphics[width=1.0\linewidth]{images/download.pdf}
 \caption{Download bandwidth utilization by the server} 
 \label{fig:download} 
\end{figure}

The results were collected as follows: to measure the average upload bandwidth usage by the server, the sizes of all packets sent during the whole session were added up and then divided by the session time; to determine the maximum usage, it was measured how many bytes had been sent each second and the highest value was selected. In Figure \ref{fig:upload}, it is shown the maximum and average upload bandwidth utilization results found for a traditional server and a \ppse{} server. In Figure \ref{fig:download}, the download bandwidth usage is also depicted. Table 1 and Table 2 show the numerical values of the average bandwidth utilization found in the simulation.

>>>>

\newcommand{\ppse}{P2PSE}
\newcommand{\hoverkill}{Hoverkill}

@@

% \author{JEMS Manuscript Number 48534}
% \contactinfo{48534@JEMS}
%% Author and Affiliation (multiple authors). Use: and between authors
\author{Felipe J. Vilanova, Carlos Eduardo B. Bezerra , Marcos R. Crippa, Fábio R. Cecin, Cláudio F. R. Geyer\\
          Universidade Federal do Rio Grande do Sul\\
          Bento Gonçalves, 9500\\
          Porto Alegre, RS, Brazil\\
          +55 (51) 3316 0000
}
\contactinfo{\{fjvilanova, carlos.bezerra, mrcrippa, fcecin, geyer\}inf.ufrgs.br}

@@

Multiplayer games are a very popular game genre, due to their highly interactive nature. Among those games, a class that is growing in popularity is MMOGs (Massively Multiplayer Online Games). MMOGs are real-time multiplayer games played through the Internet, where a large number of players (usually thousands) play within a persistent-state virtual world. Successful examples include EverQuest \cite{everquest} and World of Warcraft \cite{worldofwarcraft}.

@@

The main disadvantage of the client-server model is the lack of scalability. The cost of maintaining the server-side becomes excessive with the increase in the number of clients. When it comes to commercial games, the usual approach is to continuously expand the number of machines on the server-side. That is a reasonable solution, however it is not suitable for projects on a limited budget such as those from small companies or research groups.

@@

In this paper a hybrid model is proposed, combining the security and consistency of the client-server model with the scalability and flexibility of the distributed model. In sections \ref{sec:c-smodel} and \ref{sec:p2pmodel} we discuss the client-server and peer-to-peer models. The \ppse{} (acronym in portuguese for ``P2P for Entertainment Software'') architecture is explained in section \ref{sec:p2pse}. Section \ref{sec:simulations} presents the simulations we made to compare client-server and peer-to-peer models. Section \ref{sec:conclusion} presents conclusions on the topic.

@@

There is a growing interest in research and development of peer-to-peer architectures for MMOGs. The proposed models seek decentralization as a way of increasing scalability and reducing dependency on nodes in trusted areas. Other benefits include the elimination of central points of failure, as well as the increase of responsiveness.

@@

Guild Wars, as far as we can tell, follows the client-server model. Our proposal, which is illustrated in Figure \ref{fig:instanced}, is to use the instanced game model with a hybrid network architecture model. Since the interactions on the social space (chatting, trading) don't require high consistency, and there is a necessity for validation of who can play (game accounts, passwords), the server-side will be responsible for coordinating this part of the game. So even a server-side with modest processing capacity and network bandwidth could manage the social space if game quality is scaled down accordingly, for instance by sending less frequent updates to clients. The game sessions would be processed only on the client-side machines, avoiding unnecessary processing and communication cost on the server-side. The clients would form groups, which would operate within a peer-to-peer dynamics.

@@

\begin{figure}[h]
  \centering 
  \includegraphics[width=0.7\linewidth]{images/p2pse.pdf}
 \caption{\ppse{} Architecture} 
 \label{fig:p2pse} 
\end{figure}

@@

The first layer in the \ppse{} architecture is responsible for forming the mesh of point-to-point connections. The clients' connections with the servers and with other clients are established and managed in this layer. The basic network functions for connection establishment, such as socket creation, connection and packet sending and receiving, are given by a low-level API provided by the ZIG library \cite{zige} which basically implements a protocol that resembles SCTP \cite{stewart2000sct} over UDP. The term ``connection'', when used in the context of the \ppse{} library, refers to this ZIG-layer level protocol connection, which, again, is implemented over UDP, adding some features, such as reliability, timeout detection and utilization of only one single socket in every host to handle all communications.

The Layer 0 server is responsible for managing connections with all clients. Naturally, it maintains a list of all clients that are connected to it along with a logical communication endpoint object for each client. When started, the server spawns a socialization space called the social space object. The clients that are not in an action space are bound to the social space - or to the ``limbo'', when in transit from one space to the other. All communication between clients that are in the social space is intermediated by the server.

The server can create new empty groups in order to instantiate new action spaces, or destroy such existing groups and their corresponding spaces. In the action spaces all the clients communicate directly, which requires them to already have the ability to send UDP packets to one another. The entry of a client into a group is managed by the server in the following manner:

\begin{enumerate}
\item The server sends a synchronization message to the new member and to all the other members informing them to which clients they must be connected in order to enter (or stay) in the group. The server sends a list with all the members of the group;
\item All members try then to establish connections to every other member in the recently received member list, or just keep the connection, if it has already been established (the ZIG library supports simultaneous bidirectional connections through the same socket);
\item When a client is entering a group, but still has not finished the process, it belongs to the ``limbo'';
\item As soon as the new member establishes connections to the other clients, the server excludes it from the limbo and inserts it in the member list of the group;
\item When a client is removed from the group, all connections to the other clients are interrupted and it returns to the social space;
\item If a client, for any reason, loses its connection to the server, it is removed from the group;
\item When a client enters or leaves a group, the server sends to the others  an up-to-date member list.
\end{enumerate}

The groups provide to the clients message exchanging functionalities, such as broadcast and unicast. The connections between the group members are represented by peers. The clients, when in groups, will keep a list of peers, what is equivalent to the client list of the server. With this list, the clients in that group manage their connections between one another.

Layer 0 is also responsible for the timeout control of the connections. Keep-alive dummy messages are sent regularly in order to maintain all connections active. If, after an interval of time specified by the application, no messages from a host have arrived, the connection to that host is closed.

The communication between the layer 0 and the ZIG library is done with a listener. This listener is implemented in layer 0 and receives ZIG callbacks to indicate the occurrence of events such as connections, disconnections and receiving of messages. The communication between the upper layers of the \ppse{} library and layer 0 is made through service calls. Layer 0 returns callbacks to the upper layers in response to these service calls.

@@

We see two main problems that can cause a connection failure between two peers: NAT/Firewall blocking and bandwidth insufficiency. When the Layer 0 indicates that a message must be sent from one peer to another, Layer 1 must verify if there is a direct connection between the peers. If this connection doesn't exist, an alternative path must be discovered, using intermediate peers. After this route is created, the messages will be sent through it.

@@

Depending on the game, the resulting conflicts from a lack of centralized timestamping of movement and similar events, whenever they ensue, can be either handled by each peer individually or left for the super-peer to detect it and issue a special correction message later, as the BZFlag protocol does \cite{pellegrino2003bra}. Local corrections are an option if each peer is authoritative over its own avatar's position and if it broadcasts position updates for its own avatar. For instance, if a peer's local avatar overlaps with a remote peer's, the local avatar can push its own avatar out of that position. The remote avatar will do the same. The only issue is ensuring that the correction step won't make both peers try to resolve the situation by unstucking their avatars to the same spot again. This local conflict resolution is what we are currently employing in our capture-the-flag action prototype, \hoverkill\ \cite{hoverkill}.

@@

In this project we tried a somewhat unique approach \cite{gaspareto2008nna}. Since most events would be still centralized at the super-peer and most action games have one-per-client avatar position updates as their latency, consistency and bandwidth bottlenecks, we just left peers with total control over their positions and with the responsibility for sending them directly to other peers in a broadcast fashion. This optimizes for consistency and latency, and doesn't create a bandwidth bottleneck at the super-peer. On top of that, we tried AI-based detection of unusual patterns over streams of position updates coming from each peer. The approach used for cheat detection was focused on the data packets being transferred during the game sessions - both in the transmitters and receptors - and how they are used during the functioning of the system. Only packets relevant to the cheat being investigated are considered.

The cheat detection module is implemented in an independent way and works as an attachment to \ppse{}, which, with a parameter passage protocol, informs the set of data received from a player and returns a correspondent ``fraud index'', that tries to quantify the cheating that the player is assumed to have performed in the analyzed period.

The adopted approach was to consider only movement data as input to the cheat detection module. Although this might seem to be too few information, it is based on movement that  malicious players perform great part of their cheating. For example, one could try to move at a speed higher than the maximum speed allowed in the game (most common kind of cheating in MMOGs) or teleport instantaneously to strategic spots, which is also known as speed-cheating.

This way, the point is to analyze a set of movements of the player, in order to detect anomalous sequences. Each player will be evaluated individually, based on his position history, using Artificial Neural Networks (ANN). ANNs, because of their great generalization and pattern recognition capacity, present satisfactory results in tasks similar to the speed-cheating problem. The idea is to identify, in the set of analyzed data, at least one movement that could be considered a fraud, which characterizes the player where this set of data came from as a cheater. The ANN then identifies and classifies the movement patterns as acceptable and non-acceptable.

During the modeling and design of the cheat detection module, the architectures of the ANNs, the set of training data and the set of tests have been defined in order to allows them to solve this kind of problem. Considering that the task consists of the classification of behavior patterns, it has been decided to use the full-connected multilayer perceptron ANN with supervised learning based on back-propagation. The reason to choose it was that it is the most commonly used ANN model in many classification applications, due to it simplicity of understanding and implementation.

The projected ANN was simulated using MatLab, to evaluate its efficiency. MatLab allows the creation of complex ANN structures only by informing the neural network parameters, such as the number of neurons in each layer, training algorithm, rates, values that configure this training etc. MatLab was also used to train the ANN to be integrated to the game. This way, the implemented module only performs propagation, but not training of the ANN.

After the efficiency has been proven, the module was implemented and tested in \hoverkill{}, obtaining a 21.14\% cheat detection, and 0.98\% false positives. The results were satisfactory because, even though the cheat detection percentage was only 21.14\%, the rate of false positives was less than 1\%. It is preferable not to detect a cheat than considering a fair player as a cheater. Other parameters, besides movement data, may be added in the future, in order to detect other kinds of cheating.

@@

The main purpose of the security module is to provide secure communication between servers and clients, and between peers in an action space group. Our security module is almost completely transparent to the application, both in terms of API and in network and CPU overhead. The module does many tasks behind the scenes, such as cryptographic key distribution and secure channel handshakes, tending to each application's individual needs for message confidentiality, integrity and authenticity.

The implementation works mainly by intercepting any engine UDP packets before they are written to the UDP socket for sending. In each packet, a small header is inserted with control information and, upon first contact between two parties (being them clients, servers or both), that message is delayed while another quick message exchange is performed for setting up the secure channel on-the-fly. The root Certificate Authority (CA) of the cryptographic system is the operator of the master server.

\begin{figure}[h]
  \centering 
  \includegraphics[width=0.7\linewidth]{images/security.pdf}
 \caption{Security module architecture} 
 \label{fig:security} 
\end{figure}

The module has been implemented by extending the ZIG library functionalities, providing secure communication, transparently to the application, being responsible for distributing cryptogaphic keys. It runs over HawkNL \cite{hawknl} and over SEC\ppse{}. HawkNL is a library that, among other functionalities, provides a simpler and portable API for sockets. SEC\ppse{} is our library that provides C++ abstractions for cryptographic algorithms available in Nettle \cite{nettle} and \mbox{CyoEncode} \cite{cyoencode}. SEC\ppse{} also implements certification and serialization functionalities meant for security related transmissions. Figure \ref{fig:security} illustrates the security module architecture.%Nettle is a low-level cryptographic library written in C, which offers algorithms for hashing (MD5, SHA1, SHA256 etc.), symmetric (AES, ARCFOUR, 3DES etc.) and assymetric (HMAC-MD5, HMAC-SHA-1 and HMAC-SHA-256) cryptography and generation of pseudo-random data (Yarrow). CyoEncode \cite{cyotec} is a small library which provides coding and decoding in Base64, Base32 and Base16.

In our secure communication protocol, all ZIG-generated packets sent, both by clients and by servers, are intercepted right before being transmitted through the network. In each one of them, a small header is introduced with control information used to guarantee confidentiality, integrity and authenticity of data when such attributes are required. The size of this header is variable, for it depends on what characteristics are desired by the application, and on the intended level of security (key length). For a real-time application, such as distributed games, usually there is no need for a very long key, because the hacker would have too little time to break the algorithm by brute force. For example, using AES and HMAC-MD5, it would be necessary only 21 bytes. In general, the overhead size of each packet is somewhere between 1 and 37 bytes. These packets containing user data and control header are then called \textbf{data packets}.

There is also another type of packet, called \textbf{control packet}, which is utilized to negotiate keys between peers who intend to communicate with each other. They are usually longer, for they need to attach a copy of the users certificates. However, these packets are sent only once in the beginning of the communication with a peer which has been unknown until that moment. Once they have negotiated a key, they only need to negotiate a new one when one of the peers loses it or if the key is already being used for a time long enough for the key to become breakable by brute force.

\begin{figure}[h]
  \centering 
  \includegraphics[width=1.0\linewidth]{images/header.pdf}
 \caption{Control header} 
 \label{fig:controlheader} 
\end{figure}

The control header consists of the packet descriptor (1 byte). As shown in Figure \ref{fig:controlheader}, the bit 0 indicates whether the data are protected by HMAC-SHA-256. The bit 1 indicates whether the data are encrypted with AES. Bit 5 indicates that the message source needs the destination host certificate. Bit 6 indicates that a key has been generated and attached to the packet in control data and bit 7 indicates that the certificate of the origin has been attached to the packet in control data. Bits 2, 3 and 4 are not used.

When the application requires the secure transmission of a packet to the security library, it must inform: data being transmitted, socket used for sending, address and port of the destination, type of desired security (confidentiality, authenticity and integrity) and the identification of the user which will receive the message at the provided address.

To guarantee confidentiality of the messages, it can be used both symmetric and asymmetric cryptographic algorithms. Both are considered secure, depending on the length of the key used. The secure communication protocol adopts the strategy of initially using an asymmetric cryptography algorithm to negotiate a key to be used then by each pair of computers to communicate securely with symmetric cryptography. This approach allows to reduce the processing time of encrypting and decrypting data, for symmetric cryptography requires less CPU time. Along with the confidentiality provided by this mechanism, authenticity may also be achieved by using hash functions with keys, also known as Message Authentication Code (MAC), to verify the authenticity and integrity of the messages.

Every time that a peer needs to communicate with another which was unknown until that time, they first need to negotiate a key. Therefore, before sending the data packet required by the application, the library sends a requisition for the certificate of the destination through a control packet, which already carries the source's own certificate. When the packet arrives in the destination peer, the security library reads the attached certificate and verifies its authenticity with  the specified certification authority responsible for the game. If the verification fails, the packet is discarded. If it succeeds, the process continues: the peer who received the packet allocates a reply packet, where it attaches its own certificate, as required, and a randomly generated key, which is encrypted using the public key present in the certificate of the peer that initiated the whole process. This way, it can be assured that only the receiver of this reply packet will be able to decrypt it and then obtain the key. To guarantee that the sender of this packet is not an attacker who intercepted the communication, the already encrypted key is re-encrypted, this time with the private key of the sender. This way, both authenticity and integrity are provided.

After receiving the reply packet containing the double-encrypted key, the first peer decrypts it using the public key of the other peer, verifying the authenticity of the message, and then decrypts it again, using  its own private key. When this whole process is successfully completed, the peers will be able to securely communicate with a fast symmetric cryptographic algorithm using the generated key.

@@

\begin{figure}[h]
  \centering 
  \includegraphics[width=1.0\linewidth]{images/upload.pdf}
 \caption{Upload bandwidth utilization by the server} 
 \label{fig:upload} 
\end{figure}

\begin{figure}[h] 
  \centering 
  \includegraphics[width=1.0\linewidth]{images/download.pdf}
 \caption{Download bandwidth utilization by the server} 
 \label{fig:download} 
\end{figure}

The results were collected as follows: to measure the average upload bandwidth usage by the server, the sizes of all packets sent during the whole session were added up and then divided by the session time; to determine the maximum usage, it was measured how many bytes had been sent each second and the highest value was selected. In Figure \ref{fig:upload}, it is shown the maximum and average upload bandwidth utilization results found for a traditional server and a \ppse{} server. In Figure \ref{fig:download}, the download bandwidth usage is also depicted. Table \ref{tab:upload} and Table \ref{tab:download} show the numerical values of the average bandwidth utilization found in the simulation.

\begin{table}[h]
\caption{Average upload bandwidth utilization (kB/s)}
\centering
  \begin{tabular}{ c | c c }  
    \hline
    Clients & Traditional Server  & \ppse{} Server  \\ \hline
    40      & 1562.50             & 400.76          \\
    80      & 6250.00             & 1581.38         \\
    120     & 14062.49            & 3533.67         \\
    160     & 24999.98            & 6290.14         \\
  \hline
  \end{tabular}
\label{tab:upload}
\end{table}

\begin{table}[h]
\caption{Average download bandwidth utilization (kB/s)}
\centering
  \begin{tabular}{ c | c c }  
    \hline
    Clients & Traditional Server  & \ppse{} Server  \\ \hline
    40      & 26.04            & 13.02          \\
    80      & 52.08             & 26.04         \\
    120     & 78.12            & 39.00         \\
    160     & 104.17            & 52.09         \\
  \hline
  \end{tabular}
\label{tab:download}
\end{table}
